Appendix 2: Manuscript and Exploratory Code

### 2025-06-09 manuscript_code.Rmd
Manuscript & exploratory code

---
title: "Appendix 1: Preregistered analysis with simulated data"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  pdf_document:
    toc: yes

@@

@@

```{r}
if (fitmodels) {
  save(models,file=here("prereg_models.rdata"))
}
```

>>>>

---
title: "Appendix 2: Manuscript and Exploratory Code"
author: "Abigail Edwards, Lauri Hietajärvi and Mikko Arvas"
date: "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time())`"
output:
  pdf_document:
    toc: yes

@@

#Exploratory Analysis (Latent factor model with robust estimator and fiml)
#Exploring a1*b1 comparison

dim(factor_scores)
dim(data.fit2)

factor_scores <- lavPredict(fit.po04, type = "lv")
head(factor_scores)
summary(factor_scores)

df_scores <- cbind(
  as.data.frame(factor_scores),
  de02 = data.fit2$de02,
  de01 = data.fit2$de01
)

ggplot(df_scores, aes(x = psycown, y = intention,
                      color = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "gender") +
  theme_minimal()

ggplot(df_scores, aes(x = p, y = intention,
                      color = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "gender") +
  theme_minimal()

ggplot(df_scores, aes(x = psycown, y = intention,
                      color = as.factor(de02),
                      shape = as.factor(de01))) +
  geom_point(alpha = 0.7, size = 2.5) +
  labs(title = "Latent Factor Scores by de01 and de02",
       x = "Psychological Ownership",
       y = "Donation Intention",
       color = "age",
       shape = "gender") +
  theme_minimal()

@@

```{r}
if (fitmodels) {
  save(models,file=here("prereg_models.rdata"))

}
```
